Brainstorm for Ch3

### 2022-02-04 Ch3_samplesize/ideafeb4.Rmd
Brainstorming

---
title: "Mixture distribution data generation"
author: "Javiera Rudolph"
date: "1/20/2022"
output:
  html_document:
  toc: true
---

@@

1.    The sampling scheme should have this variation between individuals and number of observations per individual. *What are we sampling? locations?*  
2.

>>>>

---
title: "Brainstorm for Ch3"
author: "Javiera Rudolph"
date: "2/4/2022"
output:
  html_document:
  toc: true
---

@@

1.    The sampling scheme should have this variation between individuals and number of observations per individual. *What are we sampling? locations? of individuals or the seeds?*  
    *       We are trying to answer if it is better to sample 3 individuals and follow them for months, getting 100s of observations for each individual.  
    *       OR if it is better that we sample 10 or 20 individuals, and follow them for a couple of weeks only and get maybe only 30, 50 observations for each.

      **My guess, is that it will be better to sample more individuals for shorter time frames, because the question is trying to capture these long distance movements which may vary by individual.**

2.   We use
